Non-kissing versus non-crossing

### 2018-11-05 secondPaper/FPSAC/figures/lozenge.tex
FPSAC

\documentclass{amsart}

\usepackage[T1]{fontenc}
\usepackage{enumerate, amsmath, amsfonts, amssymb, amsthm, mathrsfs, wasysym, graphics, graphicx, xcolor, url, hyperref, hypcap, xargs, multicol, pdflscape, multirow, hvfloat, array, ae, aecompl, pifont, mathtools, a4wide, float, blkarray}
\usepackage{marginnote}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue}
\usepackage[all]{xy}
\usepackage{tikz}
\usepackage{tkz-graph}
\usetikzlibrary{trees, decorations, decorations.markings, shapes, arrows, matrix, calc, fit, intersections, patterns, angles}
\graphicspath{{figures/}}
\makeatletter\def\input@path{{figures/}}\makeatother
\usepackage{caption}
\captionsetup{width=\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% theorems
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{convention}[theorem]{Convention}

% math special letters
\newcommand{\R}{\mathbb{R}} % reals
\newcommand{\N}{\mathbb{N}} % naturals
\newcommand{\Z}{\mathbb{Z}} % integers
\newcommand{\C}{\mathbb{C}} % complex
\newcommand{\I}{\mathbb{I}} % set of integers
\newcommand{\HH}{\mathbb{H}} % hyperplane
\newcommand{\K}{k} % field
\newcommand{\fA}{\mathfrak{A}} % alternating group
\newcommand{\fS}{\mathfrak{S}} % symmetric group
\newcommand{\cA}{\mathcal{A}} % algebra
\newcommand{\cC}{\mathcal{C}} % collection
\newcommand{\cS}{\mathcal{S}} % ground set
\newcommand{\uR}{\underline{R}} % underline set
\newcommand{\uS}{\underline{S}} % underline set
\newcommand{\uT}{\underline{T}} % underline set
\newcommand{\oS}{\overline{S}} % overline set
\newcommand{\ucS}{\underline{\cS}} % underline ground set
\renewcommand{\b}[1]{\mathbf{#1}} % bold letters
\newcommand{\h}{\widehat} % hat letters

% math commands
\newcommand{\set}[2]{\left\{ #1 \;\middle|\; #2 \right\}} % set notation
\newcommand{\bigset}[2]{\big\{ #1 \;\big|\; #2 \big\}} % big set notation
\newcommand{\Bigset}[2]{\Big\{ #1 \;\Big|\; #2 \Big\}} % Big set notation
\newcommand{\setangle}[2]{\left\langle #1 \;\middle|\; #2 \right\rangle} % set notation
\newcommand{\ssm}{\smallsetminus} % small set minus
\newcommand{\dotprod}[2]{\left\langle \, #1 \; \middle| \; #2 \, \right\rangle} % dot product
\newcommand{\symdif}{\,\triangle\,} % symmetric difference
\newcommand{\one}{{1\!\!1}} % the all one vector
\newcommand{\eqdef}{\mbox{\,\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}}\ensuremath{=}\,}} % :=
\newcommand{\defeq}{\mbox{~\ensuremath{=}\raisebox{0.2ex}{\scriptsize\ensuremath{\mathrm:}} }} % =:
\newcommand{\simplex}{\triangle} % simplex
\renewcommand{\implies}{\Rightarrow} % imply sign
\newcommand{\transpose}[1]{{#1}^t} % transpose matrix

% operators
\DeclareMathOperator{\conv}{conv} % convex hull
\DeclareMathOperator{\vect}{vect} % linear span
\DeclareMathOperator{\cone}{cone} % cone hull
\DeclareMathOperator{\inv}{inv} % inversions
\DeclareMathOperator{\ascents}{asc} % ascents
\DeclareMathOperator{\descents}{des} % descents

% others
\newcommand{\fref}[1]{Figure~\ref{#1}} % reference figures
\newcommand{\ie}{\textit{i.e.}~} % id est
\newcommand{\eg}{\textit{e.g.}~} % exempli gratia
\newcommand{\Eg}{\textit{E.g.}~} % exempli gratia
\newcommand{\apriori}{\textit{a priori}} % a priori
\newcommand{\viceversa}{\textit{vice versa}} % vice versa
\newcommand{\versus}{\textit{vs.}~} % versus
\newcommand{\aka}{\textit{a.k.a.}~} % also known as
\newcommand{\perse}{\textit{per se}} % per se
\newcommand{\ordinal}{\textsuperscript{th}} % th for ordinals
\newcommand{\ordinalst}{\textsuperscript{st}} % st for ordinals
\definecolor{darkblue}{rgb}{0,0,0.7} % darkblue color
\definecolor{green}{RGB}{57,181,74} % green color
\definecolor{violet}{RGB}{147,39,143} % violet color
\newcommand{\red}{\color{red}} % red command
\newcommand{\green}{\color{green}} % green command
\newcommand{\darkblue}{\color{darkblue}} % darkblue command
\newcommand{\defn}[1]{\textsl{\darkblue #1}} % emphasis of a definition
\newcommand{\para}[1]{\medskip\noindent\textit{#1.}} % paragraph
\renewcommand{\topfraction}{1} % possibility to have one page of pictures
\renewcommand{\bottomfraction}{1} % possibility to have one page of pictures
\newcommand{\ex}{_{\textrm{exm}}} % examples
\newcommand{\pa}{_{\textrm{pa}}} % path
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=1pt, scale=.7] (char) {#1};}}

% marginal comments
\usepackage{todonotes}
\newcommand{\yann}[1]{\todo[color=red!30]{#1 --- Y.}}
\newcommand{\vincent}[1]{\todo[color=blue!30]{#1 \\ \hfill --- V.}}
\newcommand{\pierreguy}[1]{\todo[color=green!30]{#1 \\ \hfill --- PG.}}

% SPECIFIC NON-KISSING COMPLEX

% COMBINATORICS
% quiver
\newcommand{\blossom}{^\text{\ding{96}}} % blossom
\newcommand{\Enrs}[1]{E_{nr}^{s}(#1)}
\newcommand{\Ers}[1]{E_{r}^{s}(#1)}
\newcommand{\Enrt}[1]{E_{nr}^{t}(#1)}
\newcommand{\Ert}[1]{E_{r}^{t}(#1)}

% walks
\newcommand{\peaks}[1]{\mathsf{peaks}(#1)} % peaks
\newcommand{\deeps}[1]{\mathsf{deeps}(#1)} % deeps
\newcommand{\distinguishedWalk}[2]{\mathsf{dw}(#1,#2)} % distinguished walk
\newcommand{\distinguishedArrows}[2]{\mathsf{da}(#1,#2)} % distinguished arrows
\newcommand{\distinguishedString}[2]{\mathsf{ds}(#1,#2)} % distinguished string
\newcommand{\distinguishedSign}[2]{\varepsilon(#1,#2)} % distinguished sign

% non-kissing complex, lattice, flip graph
\newcommand{\kn}{\kappa} % kissing number
\newcommand{\KN}{\textsc{kn}} % Kissing Number
\newcommandx{\NKC}[1][1=\bar Q]{\mathcal{K}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\RNKC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nk}}(#1)} % non-kissing complex
\newcommandx{\NKL}[1][1=\bar Q]{\mathcal{L}_{\mathrm{nk}}(#1)} % non-kissing lattice
\newcommandx{\NKG}[1][1=\bar Q]{\mathcal{G}_{\mathrm{nk}}(#1)} % non-kissing flip graph
\newcommandx{\NFC}[1][1=\bar Q]{\mathcal{C}_{\mathrm{nf}}(#1)} % non-friendly complex
\newcommand{\peak}{\mathrm{peak}} % bottom dissection
\newcommand{\deep}{\mathrm{deep}} % top dissection
\newcommand{\reversed}[1]{#1^{\mathrm{rev}}} % reverse all arrows
\renewcommand{\top}{\mathrm{top}} % top
\newcommand{\bottom}{\mathrm{bot}} % bottom
\newcommand{\walk}{\operatorname{\omega}} % walk (of a curve)

% accordion and slalom complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\vertices}{\mathcal{V}} % vertices of a dissection
\newcommand{\edges}{\mathcal{E}} % edges of a dissection
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\RAC}[1][1=\dissection]{\mathcal{C}_{\mathrm{acc}}(#1)} % reduced accordion complex
\newcommandx{\SC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{sla}}(#1)} % slalom complex
\newcommandx{\RSC}[1][1=\dissection\dual]{\mathcal{C}_{\mathrm{sla}}(#1)} % reduced slalom complex
\newcommandx{\NCC}[1][1={\dissection, \dissection\dual}]{\mathcal{K}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommandx{\RNCC}[1][1={\dissection, \dissection\dual}]{\mathcal{C}_{\mathrm{nc}}(#1)} % non-crossing complex
\newcommand{\curveof}{\operatorname{\gamma}} % curve (of a walk)
\newcommand{\edgeof}{\operatorname{\varepsilon}} % arc of a vertex
\newcommand{\dualedgeof}{\operatorname{\varepsilon}\dual} % dual arc of a vertex
\DeclareRobustCommand{\SSS}{\reflectbox{$\mathsf{Z}$}} % S
\DeclareRobustCommand{\ZZZ}{\mathsf{Z}} % Z
\newcommand{\vnext}[1]{#1_{\operatorname{next}}} % next point on the boundary of the surface
\newcommand{\vprevious}[1]{#1_{\operatorname{prev}}} % previous point on the boundary of the surface

% lattices
\newcommand{\meet}{\wedge} % meet
\newcommand{\join}{\vee} % join
\newcommand{\bigMeet}{\bigwedge} % meet
\newcommand{\bigJoin}{\bigvee} % join
\newcommand{\closure}[1]{#1^{\mathrm{cl}}} % closure operator
\newcommand{\coclosure}[1]{#1^{\mathrm{cocl}}} % coclosure operator
\newcommand{\uclosure}[1]{#1^{\underline{\mathrm{cl}}}} % loop free closure operator
\newcommand{\Bicl}[1]{\mathsf{Bic}(#1)} % biclosed sets
\newcommand{\projDown}{\pi_\downarrow} % down projection map
\newcommand{\projUp}{\pi^\uparrow} % up projection map
\newcommand{\JI}{\mathsf{JI}} % join-irreducible
\newcommand{\MI}{\mathsf{MI}} % meet-irreducible
\newcommand{\Cong}{\mathsf{Cong}} % congruence lattice
\newcommand{\con}{\mathrm{con}} % congruence contracting a cover relation
\newcommand{\ji}{\mathsf{ji}} % join irreducible
\newcommand{\mi}{\mathsf{mi}} % meet irreducible

% GEOMETRY
% d-vectors
\newcommand{\dvector}[1]{\mathbf{d}(#1)} % d-vector of the path #1
\newcommand{\dvectors}[1]{\mathbf{d}(#1)} % d-vectors of the paths #1
\newcommandx{\dvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{d}(#1)} % d-vector fan
% g-vectors
\newcommand{\gvector}[1]{\mathbf{g}(#1)} % g-vector of the path #1
\newcommand{\gvectors}[1]{\mathbf{g}(#1)} % g-vectors of the paths #1
\newcommandx{\gvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{g}(#1)} % g-vector fan
% c-vectors
\newcommand{\cvector}[2]{\mathbf{c}(#1 \in #2)} % c-vector of the path #1 in the facet #2
\newcommand{\cvectors}[1]{\mathbf{c}(#1)} % c-vectors of the paths #1
\newcommandx{\allcvectors}[1][1=\bar Q]{\mathbf{C}(#1)} % all c-vectors with respect to the initial cluster #1
\newcommandx{\cvectorFan}[1][1=\bar Q]{\mathcal{F}^\mathbf{c}(#1)} % fan of hyperplanes orthogonal to all c-vectors
% points, hyperplanes, half-spaces
\newcommand{\point}[1]{\mathbf{p}(#1)} % vertex of the grid associahedron corresponding to the cluster #1
\newcommand{\ray}{\mathbf{r}} % ray
\newcommand{\rays}{\mathbf{R}} % rays
\newcommand{\hs}{\mathbf{H}^{\le}} % half space
\newcommand{\HS}[1]{\mathbf{H}^{\le}(#1)} % half space
\newcommand{\hyp}{\mathbf{H}^{=}} % hyperplane
\newcommand{\Hyp}[1]{\mathbf{H}^{=}(#1)} % hyperplane
\newcommand{\fix}[1]{\mathrm{Fix}(#1)} % fix space
% polytopes
\newcommandx{\Asso}[2][1=\bar Q,2={}]{\mathsf{Asso}^{#2}(#1)} % associahedron
\newcommandx{\Zono}[2][1=\bar Q,2={}]{\mathsf{Zono}^{#2}(#1)} % zonotope
\newcommand{\Fan}{\mathcal{F}} % fan
\newcommand{\multiplicityVector}{\b{m}} % multiplicity vector

% ALGEBRA
\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
\newcommandx{\AR}[1][1=\bar Q]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
\newcommandx{\tTC}[1][1=\bar Q]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
\newcommand{\rep}{\operatorname{{\rm rep}}}
\newcommand{\proj}{\operatorname{{\rm proj}}}
\newcommand{\koszul}{^!} % duality

%% formating the part command
%\makeatletter
%\def\part{\@startsection{part}{1}%
%\z@{.7\linespacing\@plus\linespacing}{.8\linespacing}%
%{\LARGE\sffamily\centering}}
%\@addtoreset{section}{part}
%\makeatother
%\renewcommand{\thesection}{\arabic{part}.\arabic{section}}

% formating the table of contents
\makeatletter
\def\l@section{\@tocline{1}{2pt}{0pc}{}{}}
\makeatother
\let\oldtocpart=\tocpart
\renewcommand{\tocpart}[2]{\bf\large\oldtocpart{#1}{#2}}
\let\oldtocsection=\tocsection
\renewcommand{\tocsection}[2]{\bf\oldtocsection{#1}{#2}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Non-kissing and non-crossing complexes for locally gentle algebras]{Non-kissing and non-crossing complexes \\ for locally gentle algebras}

\thanks{YP, VP and PGP were partially supported by the French ANR grant SC3A~(15\,CE40\,0004\,01). VP was partially supported by the French ANR grant CAPPS~(17\,CE40\,0018).}

\author{Yann Palu}
\address[Yann Palu]{LAMFA, Universit\'e Picardie Jules Verne, Amiens}
\email{yann.palu@u-picardie.fr}
\urladdr{\url{http://www.lamfa.u-picardie.fr/palu/}}

\author{Vincent Pilaud}
\address[Vincent Pilaud]{CNRS \& LIX, \'Ecole Polytechnique, Palaiseau}
\email{vincent.pilaud@lix.polytechnique.fr}
\urladdr{\url{http://www.lix.polytechnique.fr/~pilaud/}}

\author{Pierre-Guy Plamondon}
\address[Pierre-Guy Plamondon]{Laboratoire de Math\'ematiques d'Orsay, Universit\'e Paris-Sud, CNRS, Universit\'e Paris-Saclay}
\email{pierre-guy.plamondon@math.u-psud.fr}
\urladdr{\url{https://www.math.u-psud.fr/~plamondon/}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{abstract}
Starting from a locally gentle bound quiver, we define on the one hand a simplicial complex, called the non-kissing complex.
On the other hand, we construct a punctured, marked, oriented surface with boundary, endowed with a pair of dual dissections.
From those geometric data, we define two simplicial complexes: the accordion complex, and the slalom complex, generalizing work of A. Garver and T. McConville in the case of a disk.
We show that all three simplicial complexes are isomorphic, and that they are pure and thin.
In particular, there is a notion of mutation on their facets, akin to $\tau$-tilting mutation.
Along the way, we also construct inverse bijections between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of punctured, marked, oriented surfaces with boundary, endowed with a pair of dual dissections.
\end{abstract}

\vspace*{-1.3cm}
\maketitle
\vspace{-.7cm}

\section{Introduction}

\enlargethispage{.1cm}
The aim of this paper is to prove that two combinatorial objects, called the \emph{non-kissing complex} and the \emph{non-crossing complex}, are isomorphic.
Both complexes appeared in different works in specific cases: the non-kissing complex of a grid appeared in \cite{McConville}, while the non-crossing complex of a disk appeared in \cite{GarverMcConville, MannevillePilaud-accordion}.
It was shown in \cite{PaluPilaudPlamondon} that these complexes are special cases of a more general simplicial complex, defined for any gentle algebra (see also~\cite{BrustleDouvilleMousavandThomasYildirim}).

In order to unify these two objects, we are lead to introduce two generalizations.
On the algebraic side, the non-kissing complex is extended from the class of gentle algebras to that of locally gentle algebras (which are an infinite-dimensional version of gentle algebras).
On the geometric side, we construct the non-crossing complex of an arbitrary oriented punctured surface endowed with a pair of dual dissections.

The two main objects of our study will thus be locally gentle algebras and dissections of surfaces.
Our first main result is that these two classes of objects are essentially the same.

\begin{theorem*}[\ref{thm:bijectionLocallyGentleAndSurfaces}]
There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented punctured marked surfaces with boundary endowed with a pair of dual cellular dissections.
\end{theorem*}

On the algebraic side, we extend the study of walks from the gentle case~\cite{McConville, PaluPilaudPlamondon} to the locally gentle case, and define a notion of compatibility called non-kissing (see Section \ref{sec:nonKissingComplex}).
On the geometric side, we extend the study of dissections, accordions and slaloms from the case of the disk~\cite{GarverMcConville, MannevillePilaud-accordion} to the case of an arbitrary surface, and define a notion of compatibility called non-crossing (see Section \ref{sec:accordionSlalomNonCrossingComplexes}).
The combinatorial information contained in these notions is encoded in simplicial complexes: the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC$.

\begin{theorem*}[\ref{thm:complexesCoincide}]
The complexes~$\NKC$ and~$\NCC$ are isomorphic.
\end{theorem*}

Finally, we show in Section \ref{sec:propertiesOfComplexes} that these complexes are combinatorially very well-behaved.

\begin{theorem*}[\ref{prop:purity} and \ref{coro:thin}]
The complexes~$\NKC$ and~$\NCC$ are pure and thin.  Their dimension is computed, and mutation is explicitly described.
\end{theorem*}

We end in Section \ref{sec:vectors} with a discussion of~$\b{g}$-vectors,~$\b{c}$-vectors and~$\b{d}$-vectors associated to walks and curves.
Consequences on the representation theory of locally gentle algebras will be investigated in a future project.

Finally, let us briefly review the algebraic and geometric objects which appear in this paper.

Gentle algebras are a class of finite-dimensional associative algebras over a field, defined by generators and relations.
Their representation theory was first systematically investigated in~\cite{ButlerRingel}, and they have been thouroughly studied since.
Locally gentle algebras are obtained by dropping the requirement that gentle algebras be finite-dimensional.
It turns out that their representation theory is also well-behaved \cite{Crawley-Boevey} and that these algebras are Koszul \cite{BessenrodtHolm}.
Recently, the $\tau$-tilting theory \cite{AdachiIyamaReiten} of gentle algebras has been studied in \cite{PaluPilaudPlamondon, BrustleDouvilleMousavandThomasYildirim}.

Dissections of surfaces, on the other hand, are certain collections of pairwise non-intersecting curves on an orientable surface.
They have been defined and studied in \cite{Baryshnikov, Chapoton-quadrangulations, GarverMcConville, MannevillePilaud-accordion} in the case where the surface is an unpunctured disk.

The idea of associating a finite-dimensional algebra to a dissection (or a triangulation) of a surface seems to take its roots in the theory of cluster algebras and cluster categories.
This was first done for triangulations of polygons in \cite{CalderoChapotonSchiffler}, and then for any orientable surface with boundary in \cite{ABCP, Labardini}.  
The algebra of a dissection as we shall use it in this paper has appeared in \cite{DavidRoeslerSchiffler}.
In most of the above cases, the algebras obtained are gentle algebras.
It has also been shown in \cite{BaurCoelhoSimoes} that any gentle algebra is obtained from a dissection of a surface, and that the module category of the algebra can be interpreted by using curves on the surface.
In the case where the surface is a polygon, the $\tau$-tilting theory of the algebra of a dissection has been studied in \cite{PaluPilaudPlamondon, PilaudPlamondonStella}.

Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``framed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
Note that our dissections are always cellular, while those in \cite{BaurCoelhoSimoes} can be arbitrary.
Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich, LekiliPolishchuk}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle~algebra.

\section*{Acknowledgements}
We thank Sibylle Schroll for discussions on geometric models for gentle algebras, Salvatore Stella for discussions on accordion complexes of dissections of surfaces, and William Crawley-Boevey and Henning Krause for discussions on the representation theory of infinite dimensional algebras.

\section{Non-kissing complex}\label{sec:nonKissingComplex}

We first quickly review the definition of the non-kissing complex of a gentle bound quiver following the presentation of~\cite{PaluPilaudPlamondon} and extend it to locally gentle bound quivers.

\subsection{Locally gentle bound quivers and their blossoming quivers}

We consider a \defn{bound quiver}~$\bar Q = (Q,I)$, formed by a finite quiver~$Q$ and an ideal~$I$ of the path algebra~$kQ$ (the~$k$-vector space generated by all paths in~$Q$, including vertices as paths of length zero, with multiplication induced by concatenation of paths) such that~$I$ is generated by linear combinations of paths of length at least two.
Note that we \textbf{do not require} that the quotient algebra~$kQ/I$ be finite dimensional.
The following definition is adapted from~\cite{ButlerRingel}. We note that it is customary to consider non-finite dimensional gentle algebras in the literature, see e.g.~\cite{Schroer}.

\begin{definition}
\label{def:gentleQuiver}
A \defn{locally gentle bound quiver}~$\bar Q \eqdef (Q,I)$ is a (finite) bound quiver~where
\begin{enumerate}[(i)]
\item each vertex~$a \in Q_0$ has at most two incoming and two outgoing arrows,
\item the ideal~$I$ is generated by paths of length exactly two,
\item for any arrow~$\beta \in Q_1$, there is at most one arrow~$\alpha \in Q_1$ such that~$t(\alpha) = s(\beta)$ and~${\alpha\beta\notin I}$ (resp.~$\alpha\beta \in I$) and at most one arrow~$\gamma \in Q_1$ such that~$t(\beta) = s(\gamma)$~and~${\beta\gamma\notin I}$~(resp.~${\beta\gamma \in I}$).
\end{enumerate}
The algebra~$kQ/I$ is called a \defn{locally gentle algebra}.
A \defn{gentle bound quiver} is a locally gentle bound quiver~$\bar Q$ such that the algebra $kQ/I$ is finite-dimensional; $kQ/I$ is then a \defn{gentle algebra}.
\end{definition}

\begin{definition}
\label{def:blossomingQuiver}
A locally gentle bound quiver~$\bar Q$ is \defn{complete} if any vertex~$a \in Q_0$ is incident to either one ($a$ is a leaf) or four arrows ($a$ is an internal vertex).
The \defn{pruned subquiver} of a quiver~$\bar Q$ is the locally gentle quiver obtained by deleting all leaves of~$\bar Q$ (degree one vertices) and their incident arrows.
The \defn{blossoming quiver} of a locally gentle bound quiver~$\bar Q$ is the complete locally gentle bound quiver~$\bar Q\blossom$ whose pruned subquiver is~$\bar Q$.
The vertices of~$Q\blossom_0 \ssm Q_0$ are called \defn{blossom vertices}, and the arrows in~$Q\blossom_1 \ssm Q_1$ are called \defn{blossom arrows}.
\end{definition}

In other words, $\bar Q\blossom$ is obtained from~$\bar Q$ by adding blossom arrows and blossom vertices at each incomplete vertex of~$\bar Q$ and by completing~$I$ accordingly.
Examples are represented on \fref{fig:quivers}.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.6]{quivers}}
	\caption{Some locally gentle quivers (top) and their blossoming quivers (bottom). Initial vertices are solid and labeled while blossom vertices are hollow, and initial arrows are bold while blossom arrows are thin.}
	\label{fig:quivers}
\end{figure}

\begin{remark}
\label{rem:sizeBlossomingQuiver}
Note that~$\bar Q\blossom$ has~$2|Q_0|-|Q_1|$ incoming blossom arrows and~$2|Q_0|-|Q_1|$ outgoing blossom arrows.
Therefore, it has $|Q_0\blossom| = |Q_0| + 2(2|Q_0|-|Q_1|) = 5|Q_0|-2|Q_1|$ vertices and~${|Q_1\blossom| = |Q_1| + 2(2|Q_0|-|Q_1|) = 4|Q_0|-|Q_1|}$ arrows.
\end{remark}

\subsection{Strings and walks}

The non-kissing complex is constructed using the combinatorics of strings and walks in the quiver~$\bar Q$, whose definitions are now briefly recalled.
The terminology and notations in the following definitions is borrowed from~\cite{ButlerRingel, Crawley-Boevey}.

For any arrow~$\alpha$ of~$Q$, define a formal inverse~$\alpha^{-1}$ with the properties that~${s(\alpha^{-1}) = t(\alpha)}$, $t(\alpha^{-1}) = s(\alpha)$, $\alpha^{-1}\alpha = \varepsilon_{t(\alpha)}$ and~$\alpha\alpha^{-1} = \varepsilon_{s(\alpha)}$, where~$\varepsilon_v$ is the path of length zero starting and ending at the vertex~$v \in Q_0$.

\begin{definition}
\label{def:string}
Let~$\bar Q = (Q,I)$ be a locally gentle bound quiver.
A \defn{finite string} in~$\bar Q$ is a word of the form
\(
\rho = \alpha_1^{\varepsilon_1}\alpha_2^{\varepsilon_2}\cdots \alpha_\ell^{\varepsilon_\ell},
\)
where
	\begin{enumerate}[(i)]
	\item $\alpha_i \in Q_1$ and~$\varepsilon_i \in \{-1,1\}$ for all~$i \in [\ell]$,
	\item $t(\alpha_i^{\varepsilon_i}) = s(\alpha_{i+1}^{\varepsilon_{i+1}})$ for all~$i \in [\ell-1]$,
	\item there is no path~$\pi \in I$ such that~$\pi$ or~$\pi^{-1}$ appears as a factor of~$\rho$, and
	\item $\rho$ is reduced, in the sense that no factor~$\alpha\alpha^{-1}$ or~$\alpha^{-1}\alpha$ appears in~$\rho$, for~$\alpha \in Q_1$.
	\end{enumerate}
The integer~$\ell$ is called the \defn{length} of the string~$\rho$.
We let~$s(\rho) \eqdef s(\alpha_1^{\varepsilon_1})$ and~$t(\rho) \eqdef t(\alpha_\ell^{\varepsilon_\ell})$ denote the source and target of~$\rho$.
For each vertex~$a \in Q_0$, there is also a \defn{string of length zero}, denoted by~$\varepsilon_a$, that starts and ends at~$a$.
\end{definition}

\begin{example}
With our choice of conventions, we represent the string ${\gamma\beta^{-1}\alpha^{-1}\gamma\beta^{-1}\alpha^{-1}\gamma\delta}$ by
\[
\;\vcenter{\hbox{\includegraphics[scale=0.3]{exmString1}}}
\]
\end{example}

\begin{definition}
An oriented cycle~$c$ in~$Q$ such that~$c, c^2 \notin I$ is called \defn{primitive} if it cannot be written as an $n$-th power ($n>1$) of a cycle.
\end{definition}

\begin{notation}
If~$c$ is an oriented cycle in~$Q$ such that~$c, c^2 \notin I$, we write:
\begin{itemize}
\item $c^\infty$ for the infinite word~$c c c\cdots$,
\item ${}^\infty c$ for the infinite word~$\cdots c c c$,
\item $^\infty c^\infty$ for the bi-infinite word~$^\infty c c^\infty$.
\end{itemize}
We also define~${}^{-\infty}c \eqdef {}^{\infty}(c^{-1}) = (c^\infty)^{-1}$ and similarly~$c^{-\infty} \eqdef (c^{-1})^\infty = (^\infty c)^{-1}$.
\end{notation}

\begin{definition}
An \defn{eventually cyclic string} for~$\bar Q$ is a word~$\rho$ of the form~${}^\infty(c_1^{\varepsilon_1})\sigma (c_2^{\varepsilon_2})^\infty$, where $c_1, c_2$ are oriented cycles in~$\bar Q$ (possibly of length zero) and $\varepsilon_1, \varepsilon_2$ are signs in~$\{\pm 1\}$ such that $c_1^{2\varepsilon_1} \sigma c_2^{2\varepsilon_2}$ is a finite string in~$\bar Q$.
\end{definition}

\begin{definition}
A \defn{string} for~$\bar Q$ is a word which is either a finite string or an eventually cyclic infinite string.
We often implicitly identify the two inverse strings~$\rho$ and~$\rho^{-1}$, and call it an \defn{undirected string} of~$\bar Q$.
\end{definition}

\begin{notation}
To avoid distinguishing between finite and (bi-)infinite words, we denote strings as products~$\rho = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ where~$i < j \in \Z \cup \{\pm \infty\}$, $\varepsilon_\ell\in\{\pm 1\}$ and~$\alpha_\ell \in Q_1$ for all~$i < \ell < j$.
\end{notation}

\begin{definition}
\label{def:walk}
A \defn{walk} of a locally gentle quiver~$\bar Q$ is a maximal string of its blossoming quiver~$\bar Q \blossom$ (meaning that at each end it either reaches a blossom vertex of~$\bar Q \blossom$ or enters an infinite oriented cycle).
As for strings, we implicitly identify the two inverse walks~$\omega$ and~$\omega^{-1}$, and call it an \defn{undirected walk} of~$\bar Q$.
\end{definition}

\begin{definition}
\label{def:substrings}
A \defn{substring} of a walk~$\omega = \prod_{i < \ell < j} \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ is a string~$\sigma = \prod_{i' < \ell < j'} \alpha_\ell^{\varepsilon_\ell}$ of~$\bar Q$ for some~$i \le i' < j' \le j$, where the inequality~$i \le i'$ (resp.~$j' \le j$) is strict when~$i \ne -\infty$ (resp.~$j \ne \infty$). In other words, $\sigma$ is a factor of~$\omega$ such that
\begin{itemize}
\item the endpoints of~$\sigma$ are not allowed to be the possible blossom endpoints of~$\omega$,
\item the position of~$\sigma$ as a factor of~$\omega$ matters (the same string at a different position is considered a different substring).
\end{itemize}
Note that the string~$\varepsilon_a$ is a substring of~$\omega$ for each occurence of~$a$ as a vertex of~$\omega$.
We denote by~$\Sigma(\omega)$ the set of substrings of~$\omega$.
We use the same notation for undirected walks (of course, substrings of an undirected walk are undirected).
\end{definition}

>>>>

\begin{tikzpicture}[
	scale=1.5,
	thick,
	decoration={markings, mark=at position 0.5 with {\arrow{>}}},
	roundNode/.style={circle, fill=black, inner sep=2pt, outer sep=1.5pt}
	]
	\node[roundNode, label={[label distance=-3pt]left:{$s(\alpha)$}}] (s) at (-1,0) {};
	\node[roundNode, label={[label distance=-3pt]right:{$t(\alpha)$}}] (t) at (1,0) {};
	\node[roundNode, fill=green, label={[label distance=-3pt]above:{$\green v(\alpha)$}}] (v) at (0,1) {};
	\node[roundNode, fill=red, label={[label distance=-3pt]below:{$\red f\dual(\alpha)$}}] (vd) at (0,-1) {};
	\draw[color=black, postaction={decorate}] (s) -> (t) node[midway, above] {$\alpha$};
	\pic [draw, angle radius=.7cm] {angle = s--t--vd};
	\pic [draw, angle radius=.7cm] {angle = vd--s--t};
	\draw[color=green, postaction={decorate}] (v) -> (s) node[midway, above left, outer sep=-3pt] {$\green \Enrs{\alpha}$};
	\draw[color=green, postaction={decorate}] (v) -> (t) node[midway, above right, outer sep=-3pt] {$\green \Enrt{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (s) node[midway, below left, outer sep=-3pt] {$\red \Ers{\alpha}$};
	\draw[color=red, postaction={decorate}] (vd) -> (t) node[midway, below right, outer sep=-3pt] {$\red \Ert{\alpha}$};
\end{tikzpicture}
